Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-11-15 Articles/Article 1/main.tex
minor improvements

% JUST RIGHT
Our method \remove{innovatively} employs inverse kinematics approach (IK) to guide the end effector (EE) towards its target, marking a departure from Khatib's joint coordinate approach in favor of a Cartesian coordinate framework. This is particularly beneficial in scenarios involving redundant manipulators, where determining an optimal goal joint configuration in advance is challenging.

@@

\begin{equation} 
	\vec{v}_{ATT} = \frac{\vec{x}_{EE} - \vec{x}_g}{||\vec{x}_{EE} - \vec{x}_g||} \times \frac{\arctan(k_{sigm} \; ||\vec{x}_{EE} - \vec{x}_g||) }{pi/2}
	\label{eq: v_att}
\end{equation}

In the above equation (eq.~\ref{eq: v_att}), $\vec{v}_{ATT}$  represents the end effector's translational velocity towards the target, combining direction and magnitude. The terms $\vec{x}_{EE}$ and $\vec{x}_g$ denote the current and goal positions of the EE, respectively, in Cartesian coordinates. The unit vector calculation, $\frac{\vec{x}_{EE}-\vec{x}_g}{||\vec{x}_{EE}-\vec{x}_g||}$, ensures motion directed towards the target. Finally, the sigmoid function, particularly the arctangent component, modulates this velocity to avoid overshooting, balancing speed and precision. The constant $k_{sigm}$ allows us to set how close to the goal does the robot EE start slowing down.

>>>>

\add{
	-equation references \\
	- citations \\
	- check if quat log equation is correct
}

% JUST RIGHT
Our method \remove{innovatively} employs inverse kinematics approach (IK) to guide the end effector (EE) towards its target, marking a departure from Khatib's joint coordinates approach in favor of a Cartesian coordinates framework. This is particularly beneficial in scenarios involving redundant manipulators, where determining an optimal goal joint configuration in advance is challenging.

@@

\begin{equation} 
	\vec{v} = \frac{\vec{x}_{EE} - \vec{x}_g}{||\vec{x}_{EE} - \vec{x}_g||} \times \frac{\arctan(k_{sigm} \; ||\vec{x}_{EE} - \vec{x}_g||) }{pi/2}
	\label{eq: v_att}
\end{equation}

In the above equation (eq.~\ref{eq: v_att}), $\vec{v}$  represents the end effector's translational velocity towards the target, combining direction and magnitude. The terms $\vec{x}_{EE}$ and $\vec{x}_g$ denote the current and goal positions of the EE, respectively, in Cartesian coordinates. The unit vector calculation, $\frac{\vec{x}_{EE}-\vec{x}_g}{||\vec{x}_{EE}-\vec{x}_g||}$, ensures motion directed towards the target. Finally, the sigmoid function, particularly the arctangent component, modulates this velocity to avoid overshooting, balancing speed and precision. The constant $k_{sigm}$ allows us to set how close to the goal does the robot EE start slowing down.
